---
title: "Lab 00 - Hello IDS!"
author: "MATTHEW Hurrell"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Matthew", "Ruddy", "Herman", 
           "Abdul", "Hammish"),
  github_username = c("matthurrell", "rudyadair", "hermansokr", 
                      "7aman4013", "hamlot12"), 
  colour = c("red", "purple", "seagreen", 
             "blue", "steelblue"),
  hobby = c("Badminton", "Cricket", "Drawing", 
            "Math/Coding", "Golf"),
  favourite_number = c(6, 2, sample(10, size=1), 2, 9)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This bar chart displays the favorite numbers of each team member

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Team members", 
          y = "Favorite number",
          title = "Favorite number of each group member")
```

Labs allows you to edit the names of labels in a plot

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The reason this data visualization probably wouldn't work for all people taking the course is because there would be many, many different hobbies at 1 or 2 which would make the bar chart extremely long, and could be visualized as a pie chart which is more neat and can be analyse and displayed more easily.
